Compiling refinement types to dependent types

### 2020-07-26 tex/paper.tex
Core language values
Add most of core language evaluation rules
Mention the core evaluation rules in the text

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm{tc}{\hat\tau}
\newnonterm s s
\newnonterm l l
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}
\newnonterm{vs} \varpi

@@

\begin{figure}[ht]
  \footnotesize
  \nonterms{ec,s}
  \caption{Core language syntax}
  \label{fig:core_syntax}
\end{figure}

@@

>>>>

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm{tc}{\hat\tau}
\newnonterm s s
\newnonterm l l
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}
\newnonterm{vs} \varpi
\newnonterm{vc}{\hat\varpi}

@@

Even though we believe that our core language still enjoys the strong normalization property,
we still explicitly define the evaluation rules (\figref{core_opsem}).
Firstly, this allows fixing a specific evaluation strategy mirroring the one for the surface language,
simplifying the subsequent proofs of some key theorems.
Secondly, the rule for \textsc{CE-CaseMatch},
as well as our flavour of pattern matching in general,
deserves some special attention.
\todo[inline]{Pay said attention.}

\begin{figure}[ht]
  \footnotesize
  \nonterms{ec,s,vc}
  \caption{Core language syntax}
  \label{fig:core_syntax}
\end{figure}

@@

\begin{figure}[ht]
  \footnotesize
  \drules[CE]{$\nonterm{ec}_1 \evalsto \nonterm{ec}_2$}{term evaluation}{AppL,AppR,AppAbs,ADT,CaseScrut,CaseMatch}
  \caption{Core language small-step operational semantics}
  \label{fig:core_opsem}
\end{figure}
